Optimal Symmetric Multimodal Templates and Concatenated Random Forests for Supervised Brain Tumor Segmentation (Simplified) with \textit{ANTsR}

### 2014-04-01 paper.tex
WIP: mild comments

\textcolor{red}{still feel unclear about it ...  does it go like this?
\begin{enumerate}
\item use tissue prior intensity models (not spatial) to initialize
  Atropos multivariate EM-MRF segmentation of new image  w/o spatial
  priors 
\item get out segmentation and posteriors ... run some shape stats on
  the segmentation 
\item separately compute the asymmetry features by mapping to the MV
  template 
\item input  asymmFeatures + atroposPosteriors + shapeFeatures to the
  RF model  ... with or w/o ground truth outcomes ?  same either way?
\end{enumerate}

@@

Application of the Stage 1 RF model results in a set of
probabilistic estimates for each of the seven tissue types.  
At the beginning of the second stage, these spatial probability maps are 
used as spatial priors in a 
MAP-MRF segmentation also performed using the Atropos 
segmentation tool \citep{avants2011} available in ANTs although we couple
it with N4 bias correction \citep{tustison2010} as contained in the script
{\tt antsAtroposN4.sh}.  The probabilistic segmentation output and corresponding
connected-component feature images for each modality replace the analogous 
GMM-based feature images used 
during the first stage of training/prediction along with the other feature
images generated during the feature stage (such as the template-based data).
The second stage RF model is then produced similarly as the previous stage: 
\begin{align}
\label{eq:mapmrf}
\mathrm{Tissue}\,\,\mathrm{classes} \sim \sum_{i \in MAP-MRF} F_i + \sum_{i \in Asym} F_i + \sum_{i \in Misc} F_i.
\end{align}
We discovered that this composite application of random
forest models improves the resulting labeled output.

>>>>

\textcolor{red}{still feel unclear about it ...  does it go like this?
\begin{enumerate}
\item use tissue prior intensity models (not spatial) to initialize
  Atropos multivariate EM-MRF segmentation of new image  w/o spatial
  priors 
\item get out segmentation and posteriors ... run some shape stats on
  the segmentation 
\item separately compute the asymmetry features by mapping to the MV
  template 
\item input  asymmFeatures + atroposPosteriors + shapeFeatures to the
  RF model  ... with or w/o ground truth outcomes ?  same either way?
  what do you get out of the RF?
\end{enumerate}

@@

Application of the Stage 1 RF model results in a set of
probabilistic estimates for each of the seven tissue types.  
\textcolor{red}{can you say more here --- what are these in RF and R
  terms?  how the RF generate probabilities ?}
At the beginning of the second stage, these spatial probability maps are 
used as spatial priors in a 
MAP-MRF segmentation also performed using the Atropos 
segmentation tool \citep{avants2011} available in ANTs although we couple
it with N4 bias correction \citep{tustison2010} as contained in the script
{\tt antsAtroposN4.sh}.  The probabilistic segmentation output and corresponding
connected-component feature images for each modality replace the analogous 
GMM-based feature images used 
during the first stage of training/prediction along with the other feature
images generated during the feature stage (such as the template-based data).
The second stage RF model is then produced similarly as the previous stage: 
\begin{align}
\label{eq:mapmrf}
\mathrm{Tissue}\,\,\mathrm{classes} \sim \sum_{i \in MAP-MRF} F_i + \sum_{i \in Asym} F_i + \sum_{i \in Misc} F_i.
\end{align}
We discovered that this composite application of random
forest models improves the resulting labeled output.
\textcolor{red}{Is this so much a discovery or is it that the MRF
  features ``fix'' the RF output by introducing spatial coherence to
  the results .... at least , that's what it seems to me that you are
  doing ...}
